%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Wilson Resume/CV
% XeLaTeX Template
% Version 1.0 (22/1/2015)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Howard Wilson (https://github.com/watsonbox/cv_template_2004) with
% extensive modifications by Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size

\input{structure.tex} % Include the file specifying document layout

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\title{\center{Laurie M$^{c}$Clymont}} % Print the main header
\vspace{-5mm}

%------------------------------------------------

\parbox{0.5\textwidth}{ % First block
\begin{tabbing} % Enables tabbing
\hspace{2cm} \= \hspace{3cm} \= \kill % Spacing within the block
{\bf Email} \> \href{mailto:laurie_mcclymont@hotmail.com}{laurie\_mcclymont@hotmail.com} \\ % Email address
%{\bf Mobile Phone} \> +447951694231 \\ % Mobile phone
%{\bf Nationality} \> British \\ % Date of birth 
\end{tabbing}}
\hspace{2cm} % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing} % Enables tabbing
\hspace{3cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Mobile Phone} \> +447951694231 \\ % Mobile phone
\end{tabbing}}
\vspace{-10mm}\\ % Rule under the header
%%\rule{\textwidth}{0.5mm}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

%\vspace{-9mm}
\section{Personal Profile}
\begin{itemize}
\item{Physics PhD student, currently studying high-energy particle collisions at the LHC experiment at CERN.}
\item{This has given me experience of analysing and understanding large data sets with computational tools, such as Python, within
  a collaborative environment and presenting the results to a range of audiences.}
\item{My research experience, natural curiosity and strong mathematical background make me well suited to a role to using large data to tackle real-world problems.}


\end{itemize}

% Alternative
%\item{I am a physicist, studying high-energy particle collisions at the Large Hadron Collider experiment.}
%\item{This has given me experience of analysing and understanding large data sets with computational tools within
%  a collaborative environment and would like to apply these skills to real-world problems.}
%\item{I believe that my natural curiosity, computational skills, collaborative experience and strong mathematical problem solving background, make me well suited to a role in data science.}



%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------

\section{Relevant Experience}
\job
{Sep 2014 -}{Sep 2017}
{High Energy Physics Group, University College London}
{https://www.hep.ucl.ac.uk}
{PhD Candidate}
{
  \begin{itemize-noindent}
  \item{Member of the ATLAS experiment searching for new physics using large data sets.}
    \begin{itemize}
    \item{Work within many diverse teams, in an international collaboration of 3,000 scientists.}
    \item{Perform large scale data analysis projects using Python, C++ and GitHub.}
    \item{Included an 18 month long-term attachment at the main CERN campus in Geneva.} 
    \end{itemize}
  \item{Lead analyser measuring the efficiency of the ATLAS b-jet trigger.}
    \begin{itemize}
    \item{Performed a technical measurement that is essential for many analyses within the experiment.}
    \item{Involved detailed study and understanding of a complicated data-set.}
    \item{Completed measurement to relevant deadlines and results effectively communicated to collaborators.}
    \end{itemize}
  \item{ An analyser in a team searching for new physics using pairs of b-jets.}
    \begin{itemize}
    \item{Published three public results in 2016, searching for new physics in previously unexplored energies.}
    \item{Applied statistical techniques including application of a machine learning algorithm to search for new physics.}
    \item{Validated the fit function used to predict the background in data.}
    \item{Led the use of novel data aquisition techniques to extend the reach of the search.}
    \end{itemize}
 \item{Regularly presented conclusions of data-analysis to a range of audiences.}
   \begin{itemize}
   \item{Routinely report details of analysis to technical meetings in ATLAS and at UCL.}
   \item{Selected to summarise results to large scientific audiences at international conferences and workshops.}
   \item{Involved in public outreach explaining current research to non-physicists, including school visits.}
   \end{itemize}
 \end{itemize-noindent}
}
%------------------------------------------------
\job
{June 2012 -}{Sep 2012}
{Institute of Astronomy, University of Cambridge}
{http://www.ast.cam.ac.uk}
{Summer Research Intern}
{\begin{itemize-noindent}
  \item{Spent eight weeks during the summer analysing data from two large astronomical telescopes.}
  \item{Used a statistical profile likelihood method to identify possible ``quasar'' candidates for further study.}
\end{itemize-noindent}}

\job
{Oct 2010 -}{Oct 2011}
{Merton College, University of Oxford}
{}
{Student Access Representative}
{\begin{itemize-noindent}
  \item{Liaised with schools to help organise visits and encourage applications from a wide range of backgrounds.}
  \item{Led a group of students to producing an alternative prospectus advertising the college to potential applicants.}
 \end{itemize-noindent}}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
\edu
{2010-14}
{Merton College, University of Oxford}
{https://www.merton.ox.ac.uk/node/111}
{
  \begin{itemize-noindent}
  \item{MPhys Physics - 2:1 (68\%)}
  \item{Involved mathematical problem solving for a range of situations; e.g general relativity and particle physics.}
  \end{itemize-noindent}
}

\edu
{2004-10}
{Altrincham Grammar School For Boys}
{https://www.agsb.co.uk}
{
  \begin{itemize-noindent}
  \item{A-Levels: Maths, Further Maths, Physics, History (A*, A* , A*, B).}
  \end{itemize-noindent}
}

%------------------------------------------------



%----------------------------------------------------------------------------------------
%	IT/COMPUTING SKILLS SECTION
%----------------------------------------------------------------------------------------
\vspace{-3mm}
\section{Programming Skills}
\begin{tabbing}
  \hspace{2mm} \= \hspace{18mm} \= \kill 
  \skill{Python}      {Experienced; 2 years of use in large scale data analysis.\\
                       \>\> --- Self-taught use of data-science python libraries (pandas, seaborn, scikit-learn).}
  \skill{C++}         {Experienced; 3 years of use in large scale data analysis.}
  \skill{Git}         {Experienced; 3 years of using GitHub in group and private analysis projects.}
  \skill{SQL}         {Basic; Self taught using online tutorials and private projects.}
  \skill{Misc.}       {Experienced user of Excel, PowerPoint, LaTeX, Word, Bash and Linux terminal.}
\end{tabbing}

%------------------------------------------------


%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------
\vspace{-9mm}
\section{Interests}

\begin{tabbing}
  \hspace{2mm} \= \hspace{18mm} \= \kill 
  \skill{Sports}   {Play regularly in a local cricket and 5-a-side football team. Keen runner and cyclist.}
  \skill{French}   {Conversational level. Practice through weekly in person conversations with french natives for 2 years.}
  \skill{Travel}   {Enjoy exploring new cities and countries and their cultures.}
\end{tabbing}

\vspace{-4mm}
Referees available upon request


\end{document}

%----------------------------------------------------------------------------------------
%	END OF CV
%----------------------------------------------------------------------------------------

\newpage

%----------------------------------------------------------------------------------------
%	OTHER IDEAS
%----------------------------------------------------------------------------------------

\section{Ideas of Other Relevant Experience}

\job
{June 2013 -}{Sep 2013}
{Rutherford-Appleton Laboratory, Didcot}
{}
{Summer Research Intern}
{\begin{itemize-noindent}
  \item{Spent eight weeks analysing a particular new physics model using a C++ framework.}
  \item{Identified an angular variable could be used to seperate signal from background.}
\end{itemize-noindent}}

\job
{Oct 2010 -}{Oct 2011}
{Merton College JCR Access Representative}
{}
{}
{\begin{itemize-noindent}
  \item{Interacted with school students to encourage applications from a wide range of backgrounds to the college.}
  \item{Liased with officials from Merton College and schools to organise visits and encourage students.}
 \end{itemize-noindent}}

\vspace{10mm}
Still to do...
\vspace{10mm}


\job
{October 2010 -}{October 2011}
{Private projects}
{Plan to do...}
{}
{\begin{itemize-noindent}
  \item{Used random-trees algorithm to predict survival of titanic passengers, using a tutorial}
  \item{More to follow}
 \end{itemize-noindent}}







%----------------------------------------------------------------------------------------
%	REFEREE SECTION
%----------------------------------------------------------------------------------------

\section{Referees}

\parbox{0.5\textwidth}{ % First block
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Bill Lumbergh \\ % Referee name
{\bf Company} \> Initech Inc. \\ % Referee company
{\bf Position} \> Vice President \\ % Referee job title 
{\bf Contact} \> \href{mailto:bill@initech.com}{bill@initech.com} % Referee contact information
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Michael "Big Mike" Tucker\\ % Referee name
{\bf Company} \> Burbank Buy More \\ % Referee company
{\bf Position} \> Store Manager \\ % Referee job title 
{\bf Contact} \> \href{mailto:mike@buymore.com}{mike@buymore.com} % Referee contact information
\end{tabbing}
}

%----------------------------------------------------------------------------------------

