%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{article} % Default font size
\input{structure.tex} % Include the file specifying document layout

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------


\parbox{0.5\textwidth}{ % First block
\title{\center{Laurie M$^{c}$Clymont}} % Print the main header
}
\hspace{2cm} % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block  
  \begin{tabbing} % Enables tabbing 
    \hspace{2cm} \= \hspace{3cm} \= \kill % Spacing within the block
           {\bf Email} \> \href{mailto:laurie.mcclymont@cern.ch}{laurie.mcclymont@cern.ch} \\ % Email address
           {\bf Mobile} \> +447951694231  \\ % Mobile phone
           {\bf LinkedIn} \> \href{https://www.linkedin.com/in/laurie-mcclymont-695520118/}{Laurie-McClymont} % LinkedIn
  \end{tabbing}
}

\rule{\textwidth}{0.5mm}

%----------------------------------------------------------------------------------------
%	PERSONAL PROFILE
%----------------------------------------------------------------------------------------

\vspace{-2mm}
\section{Personal Profile}
\begin{itemize}
\item{UCL physics PhD student, currently analysing large data sets at the LHC experiment at CERN.}
\item{Strong communication skills; including presenting complex information and collaborative working.}
\item{Experienced in using computational tools, such as Python, to analyse and understand large data sets.}
\item{My data analysis experience, natural curiosity and strong communication skills make me well
      suited to a role using large data to tackle real-world problems with Palantir Technologies.}
\end{itemize}

\vspace{0.2mm}
\rule{\textwidth}{0.5mm}

% Alternative
%\item{I am a physicist, studying high-energy particle collisions at the Large Hadron Collider experiment.}
%\item{This has given me experience of analysing and understanding large data sets with computational tools within
%  a collaborative environment and would like to apply these skills to real-world problems.}
%\item{I believe that my natural curiosity, computational skills, collaborative experience and strong mathematical problem solving background, make me well suited to a role in data science.}


%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SKILLS SECTION
%----------------------------------------------------------------------------------------
\vspace{-2mm}
\section{Skills}
\begin{tabbing}
  \hspace{3mm} \= \hspace{30mm} \= \kill 
  \skill{Computing}
        {
          Languages: Python, C++, bash. \\
          \>\>Platforms: Linux, Mac OSX. \\
          \>\>Others: Git, LaTeX, Excel, PowerPoint, Word, SQL.
        }
  \skill{Statistics}  { Regression, hypothesis testing, error analysis, machine learning, likelihoods. }
  \skill{Communication}
        {
          Selected to present at national and international conferences, involved with scientific outreach.\\
          \>\>Strong team player; worked within large teams including in a leadership role.
        }
\end{tabbing}

%------------------------------------------------

%----------------------------------------------------------------------------------------
%	EMPLOYMENT HISTORY SECTION
%----------------------------------------------------------------------------------------
\vspace{-9mm}
\section{Relevant Experience}
\job
{Sep 2014 -}{Sep 2017}
{High Energy Physics Group, University College London}
{https://www.hep.ucl.ac.uk}
{PhD Candidate}
{
  \begin{itemize-noindent}
  \item{Member of the ATLAS experiment searching for new physics using large data sets.}
    \begin{itemize}
    \item{Worked within many diverse teams, in an international collaboration of 3,000 scientists.}
    \item{Performed large scale data analysis projects using Python, C++ and GitHub.}
    \item{Included an 18 month long-term attachment at the main CERN campus in Geneva.} 
    \end{itemize}
  \item{Lead analyser measuring the efficiency of the ATLAS $b$-jet trigger.}
    \begin{itemize}
    \item{Performed a technical measurement and error analysis that is essential for the experiment.}
    \item{Identified a critical problem within the data, and developed a strategy to successfully mitigate the issue.}
    \item{Completed the measurement to deadlines and effectively communicated results to collaborators.}
    \end{itemize}
  \item{Analysis contact for a team searching for new physics using pairs of $b$-jets.}
    \begin{itemize}
    \item{Applied statistical techniques including regression, machine learning and hypothesis testing.}
    \item{Appointed analysis contact; involved co-ordinating a team of five scientists,
      liaising with experts from other groups and reporting progress and plans to management.}
    \item{Published three public results in 2016; pushing the limits of our knowledge into unexplored regions.}
    %\item{Led the use of novel data aquisition techniques to extend the reach of the search.}
    \end{itemize}
 \item{Presented conclusions of data analysis to a range of audiences.}
   \begin{itemize}
   \item{Selected to summarise results to large scientific audiences at international conferences and workshops.}
   \item{Routinely reported details of analysis to technical meetings in ATLAS and at UCL.}
   \item{Presented current research to school pupils to inspire the next generation of scientists.}
   \end{itemize}
 \end{itemize-noindent}
}
%------------------------------------------------
\job
{June 2012 -}{Sep 2012}
{Institute of Astronomy, University of Cambridge}
{http://www.ast.cam.ac.uk}
{Summer Research Intern}
{\begin{itemize-noindent}
  \item{Spent eight weeks during the summer analysing data from two large astronomical telescopes.}
  \item{Used a statistical profile likelihood method to identify possible ``quasar'' candidates for further study.}
\end{itemize-noindent}}

\job
{Oct 2010 -}{Oct 2011}
{Merton College, University of Oxford}
{}
{Student Access Representative}
{\begin{itemize-noindent}
  \item{Engaged with students from disadvantaged backgrounds to inspire and encourage applications to university.}
  \item{Led a group of students to create a prospectus, advertising the college from a student's perspective.}
 \end{itemize-noindent}}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
\edu
{2010-14}
{Merton College, University of Oxford}
{https://www.merton.ox.ac.uk/node/111}
{
  \begin{itemize-noindent}
  \item{MPhys Physics - 2:1 (68\%)}
  \item{Involved mathematical and statistical problem solving for a range of situations.}
  \end{itemize-noindent}
}

\edu
{2004-10}
{Altrincham Grammar School For Boys}
{https://www.agsb.co.uk}
{
  \begin{itemize-noindent}
  \item{A-Levels: Maths, Further Maths, Physics, History (A*, A* , A*, B).}
  \end{itemize-noindent}
}

%------------------------------------------------



%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------
\vspace{-5mm}
\section{Interests}

\begin{tabbing}
  \hspace{2mm} \= \hspace{18mm} \= \kill 
  \skill{Sports}   {Enjoy endurance sports; specifically long-distance running, cycling and cricket.}
  \skill{French}   {Conversational level. Practice through weekly in person conversations with French natives for 2 years.}
  \skill{Travel}   {Enjoy exploring new cities and countries and their cultures.}
\end{tabbing}

\vspace{-4mm}
Referees available upon request


\end{document}

%----------------------------------------------------------------------------------------
%	END OF CV
%----------------------------------------------------------------------------------------

\newpage

%----------------------------------------------------------------------------------------
%	OTHER IDEAS
%----------------------------------------------------------------------------------------

\section{Ideas of Other Relevant Experience}

\job
{June 2013 -}{Sep 2013}
{Rutherford-Appleton Laboratory, Didcot}
{}
{Summer Research Intern}
{\begin{itemize-noindent}
  \item{Spent eight weeks analysing a particular new physics model using a C++ framework.}
  \item{Identified an angular variable could be used to separate signal from background.}
\end{itemize-noindent}}

\job
{Oct 2010 -}{Oct 2011}
{Merton College JCR Access Representative}
{}
{}
{\begin{itemize-noindent}
  \item{Interacted with school students to encourage applications from a wide range of backgrounds to the college.}
  \item{Liaised with officials from Merton College and schools to organise visits and encourage students.}
 \end{itemize-noindent}}

\vspace{10mm}
Still to do...
\vspace{10mm}


\job
{October 2010 -}{October 2011}
{Private projects}
{Plan to do...}
{}
{\begin{itemize-noindent}
  \item{Used random-trees algorithm to predict survival of titanic passengers, using a tutorial}
  \item{More to follow}
 \end{itemize-noindent}}







%----------------------------------------------------------------------------------------
%	REFEREE SECTION
%----------------------------------------------------------------------------------------

\section{Referees}

\parbox{0.5\textwidth}{ % First block
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Bill Lumbergh \\ % Referee name
{\bf Company} \> Initech Inc. \\ % Referee company
{\bf Position} \> Vice President \\ % Referee job title 
{\bf Contact} \> \href{mailto:bill@initech.com}{bill@initech.com} % Referee contact information
\end{tabbing}}
\hfill % Horizontal space between the two blocks
\parbox{0.5\textwidth}{ % Second block
\begin{tabbing}
\hspace{2.75cm} \= \hspace{4cm} \= \kill % Spacing within the block
{\bf Name} \> Michael "Big Mike" Tucker\\ % Referee name
{\bf Company} \> Burbank Buy More \\ % Referee company
{\bf Position} \> Store Manager \\ % Referee job title 
{\bf Contact} \> \href{mailto:mike@buymore.com}{mike@buymore.com} % Referee contact information
\end{tabbing}
}

%----------------------------------------------------------------------------------------

